Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-12-10 tex/MISDP-Presolving/MISDPpresolving.tex
add some todos to presolving document

@@

@@

>>>>

\todo[inline]{FM: We should argue that alle the inequalities and bounds are
  as strong as possible.}

@@

\todo[inline]{FM: If we tighten the coefficients, we need to scale the
  linear constraints (for example, a trace constraint on~$A(y)$)
  accordingly.}

@@

\todo[inline]{FM: If we tighten the bounds of a variable~$y_k$, we need to
  scale the linear constraints accordingly.}
